Formalizing Stack Safety as a Security Property

### 2023-02-04 submission5/core.tex
CP

\apt{Too much real estate to sell the generality, flexibility, etc. of our approach.
  Again, we are not providing evidence that these attributes are true, although we can
  and should conjecture claim them in passing.}

@@

\begin{itemize}
\item We give a novel characterization of stack safety as a collection
of properties: confidentiality and integrity for callee and caller,
plus well-bracketed control-flow. Different subsets of these
properties characterize the security guarantees offered by mechanisms
that support only some aspects of stack safety\bcp{where do we show
  this?}.  The properties they are parameterized over a notion of
external observation, allowing them to characterize lazy enforcement
mechanisms.
\item We instantiate\bcp{extend??} these definitions in a realistic
setting with features such as\bcp{``such as''? are there others?}
argument passing on the stack, callee-saves registers, and tail-call
elimination.\bcp{How about: We extend these core definitions to
  describe a realistic setting with argument passing on the stack,
  callee-saves registers, and tail-call elimination.}  Our model is
modular enough that handling these features is straightforward.
\bcp{Throughout, the way we talk about the ``core model'' and its
  intantiation / extension / enrichment with realistic features feels
  quite weasily.}
\item We validate tag-based stack-safety enforcement via
property-based randomize testing. We find that \emph{Lazy Tagging and
  Clearing} falls short of ensuring stack safety, propose a fix, and
validate it.
\end{itemize}

Our artifact contains Coq formalizations of our properties for illustrative purposes
as well as their testing implementation. There are no proofs---we use Coq primarily
for the QuickChick library and to ensure that the formalizations are unambiguous.
Formal proofs are left as future work.

@@

The only other line of work that sets out to rigorously characterize the
security of the stack is the Cerise family of program logics
\cite{SkorstengaardLocal, SkorstengaardSTKJFP, Georges22:TempsDesCerises}.
These works define secure calling conventions for capability machines and
overlay semantics that internalize those conventions and their related stack
safety properties, phrased in terms of logical relations. Most flavors of
Cerise define experimental types of hardware capabilities in order to obtain
efficient calling conventions. Their latest result
\cite{Georges22:TempsDesCerises} uses our work to extend its notion of stack
safety to cover caller confidentiality (\(\clrc\)).

>>>>

% \apt{Too much real estate to sell the generality, flexibility, etc. of our approach.
%   Again, we are not providing evidence that these attributes are true, although we can
%   and should conjecture claim them in passing.}

@@

\begin{itemize}
\item We give a novel characterization of stack safety as a collection
of properties: confidentiality and integrity for callee and caller,
plus well-bracketed control-flow. Different subsets of these
properties characterize the security guarantees offered by mechanisms
that support only some aspects of stack safety\bcp{where do we show
  this?}.  The properties they are parameterized over a notion of
external observation, allowing them to characterize lazy enforcement
mechanisms.
\item We instantiate\bcp{extend??} these definitions in a realistic
setting with features such as\bcp{``such as''? are there others?}
argument passing on the stack, callee-saves registers, and tail-call
elimination.\bcp{How about: We extend these core definitions to
  describe a realistic setting with argument passing on the stack,
  callee-saves registers, and tail-call elimination.}  Our model is
modular enough that handling these features is straightforward.
\bcp{Throughout, the way we talk about the ``core model'' and its
  intantiation / extension / enrichment with realistic features feels
  quite weasily.}
\item We validate a tag-based stack-safety enforcement mechanism,
\emph{Lazy Tagging and Clearing}, via property-based random testing,
find that it falls short of ensuring stack safety, and propose and
validate a fix.
\end{itemize}

The accompanying artifact contains formal definitions (in Coq) of our
properties, plus our testing framework.  It does not include proofs:
we use Coq primarily for the QuickChick testing library and for
ensuring that our definitions are unambiguous.  Formal proofs are left
as future work.

@@

The only other line of work that sets out to rigorously characterize the
security of the stack is the Cerise family of program logics
\cite{SkorstengaardLocal, SkorstengaardSTKJFP, Georges22:TempsDesCerises}.
These works define secure calling conventions for capability machines and
overlay semantics that internalize those conventions and their related stack
safety properties, phrased in terms of logical relations. Most flavors of
Cerise define experimental types of hardware capabilities in order to obtain
efficient calling conventions. Their latest paper
\cite{Georges22:TempsDesCerises} uses our work to extend their notion of stack
safety to include caller confidentiality (\(\clrc\)).
